Article Title

### 2019-08-18 Paper.tex
Replace absolute genes annotated with percent value in quantity table
Added Oryza sativa gold standard
Use Frontiers template

\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={TBD},
            pdfauthor={The Pickles},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

%%% Use protect on footnotes to avoid problems with footnotes in titles
\let\rmarkdownfootnote\footnote%
\def\footnote{\protect\rmarkdownfootnote}

%%% Change title format to be more compact
\usepackage{titling}

% Create subtitle command for use in maketitle
\providecommand{\subtitle}[1]{
  \posttitle{
    \begin{center}\large#1\end{center}
    }
}

\setlength{\droptitle}{-2em}

  \title{TBD}
    \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
    \author{The Pickles}
    \preauthor{\centering\large\emph}
  \postauthor{\par}
      \predate{\centering\large\emph}
  \postdate{\par}
    \date{Febcember 32nd 3023}

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

\begin{document}
\maketitle

@@

\caption{\label{tab:cleanup_table}Number of removed annotations during cleanup.}
\centering
\begin{tabular}{llrr}
\toprule
Genome & Dataset & Obsolete Annotations & Duplicates\\
\midrule
\rowcolor{gray!6}  Triticum\_aestivum & GOMAP & 285 & 0\\
\cmidrule{1-4}
Hordeum\_vulgarum & GOMAP & 101 & 0\\
\cmidrule{1-4}
\rowcolor{gray!6}  Glycine\_max & GOMAP & 203 & 0\\
\cmidrule{1-4}
Arachis\_hypogaea & GOMAP & 0 & 0\\
\cmidrule{1-4}
\rowcolor{gray!6}  Zea\_mays.PH207 & GOMAP & 798 & 76\\
\cmidrule{1-4}
Zea\_mays.Mo17 & GOMAP & 726 & 77\\
\cmidrule{1-4}
\rowcolor{gray!6}  Phaseolus\_vulgaris & GOMAP & 0 & 0\\
\cmidrule{1-4}
Vigna\_unguiculata & GOMAP & 0 & 0\\
\cmidrule{1-4}
\rowcolor{gray!6}  Medicago\_truncatula.R108 & GOMAP & 0 & 0\\
\cmidrule{1-4}
Zea\_mays.B73.v3 & GOMAP & 1107 & 70\\
\cmidrule{1-4}
\rowcolor{gray!6}  Zea\_mays.W22 & GOMAP & 754 & 82\\
\cmidrule{1-4}
Medicago\_truncatula.A17 & GOMAP & 0 & 0\\
\cmidrule{1-4}
\rowcolor{gray!6}  Zea\_mays.B73.v4 & GOMAP & 752 & 83\\
\cmidrule{1-4}
Oryza\_sativa & GOMAP & 111 & 2\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:t_annotation_quantities}Quantitative metrics of the cleaned functional annotation sets. C, F, P, and A refer to the aspects of the GO: Cellular Component, Biological Function, Molecular Process, and Any/All.}
\centering
\resizebox{\linewidth}{!}{
\begin{threeparttable}
\begin{tabular}{lrlrrr>{\bfseries}r|rrr>{\bfseries}r|rrr>{\bfseries}r}
\toprule
\multicolumn{3}{c}{ } & \multicolumn{4}{c}{Annotations\textsuperscript{a}} & \multicolumn{4}{c}{Annotated Genes\textsuperscript{b}} & \multicolumn{4}{c}{Median Ann. per G.\textsuperscript{c}} \\
\cmidrule(l{3pt}r{3pt}){4-7} \cmidrule(l{3pt}r{3pt}){8-11} \cmidrule(l{3pt}r{3pt}){12-15}
Genome & Genes & Dataset & C & F & P & A & C & F & P & A & C & F & P & A\\
\midrule
\rowcolor{gray!6}  Arachis\_hypogaea &  & GOMAP & 153433 & 132944 & 493799 & 780176 & 57667 & 56855 & 67123 & 67124 & 2 & 2 & 6 & 10\\

Glycine\_max &  & GOMAP & 129215 & 113827 & 417555 & 660597 & 46020 & 47034 & 52871 & 52872 & 2 & 2 & 6 & 11\\

\rowcolor{gray!6}  Hordeum\_vulgarum &  & GOMAP & 88130 & 80282 & 272823 & 441235 & 35237 & 36470 & 39733 & 39734 & 2 & 2 & 5 & 10\\

Medicago\_truncatula.A17 &  & GOMAP & 107362 & 99719 & 364065 & 571146 & 42325 & 43736 & 50443 & 50444 & 2 & 2 & 6 & 10\\

\rowcolor{gray!6}  Medicago\_truncatula.R108 &  & GOMAP & 112343 & 108031 & 382322 & 602696 & 40332 & 50220 & 55706 & 55706 & 1 & 2 & 5 & 9\\

Oryza\_sativa &  & GOMAP & 72780 & 64685 & 248700 & 386165 & 28619 & 29853 & 35824 & 35825 & 2 & 2 & 6 & 9\\

\rowcolor{gray!6}  Phaseolus\_vulgaris &  & GOMAP & 72005 & 64583 & 229630 & 366218 & 25934 & 25539 & 27432 & 27433 & 2 & 2 & 6 & 11\\

Triticum\_aestivum &  & GOMAP & 267741 & 218623 & 785960 & 1272324 & 95604 & 98187 & 107890 & 107891 & 2 & 2 & 6 & 10\\

\rowcolor{gray!6}  Vigna\_unguiculata &  & GOMAP & 75867 & 68313 & 243278 & 387458 & 27173 & 27124 & 29772 & 29773 & 2 & 2 & 6 & 11\\

Zea\_mays.B73.v3 &  & GOMAP & 135211 & 87420 & 291251 & 513882 & 34866 & 38073 & 39468 & 39469 & 3 & 2 & 6 & 11\\

\rowcolor{gray!6}  Zea\_mays.B73.v4 &  & GOMAP & 88827 & 82251 & 278719 & 449797 & 36717 & 37337 & 39323 & 39324 & 2 & 2 & 6 & 10\\

Zea\_mays.Mo17 &  & GOMAP & 87567 & 79214 & 277787 & 444568 & 33618 & 35105 & 38619 & 38620 & 2 & 2 & 6 & 10\\

\rowcolor{gray!6}  Zea\_mays.PH207 &  & GOMAP & 90617 & 85500 & 288677 & 464794 & 35170 & 36762 & 40556 & 40557 & 2 & 2 & 6 & 10\\

Zea\_mays.W22 & \multirow{-14}{*}{\raggedleft\arraybackslash 100} & GOMAP & 95390 & 85039 & 289780 & 470209 & 36987 & 37685 & 40689 & 40690 & 2 & 2 & 6 & 10\\
\bottomrule
\end{tabular}
\begin{tablenotes}
\item[a] How many annotations in the C, F, and P aspect does this dataset contain? A = How many in total? $A = C + F + P$
\item[b] How many genes in the genome have at least one GO term from the C, F, P aspect annotated to them? A = How many at least one from any aspect? ($A = C \cup F \cup P$)
\item[c] Take a typical gene that is present in the annotation set. How many annotations does it have in each aspect? A = How many in total? Ask your favorite statistician why $A \neq C + F +P$
\end{tablenotes}
\end{threeparttable}}
\end{table}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% This is just an example/guide for you to refer to when submitting manuscripts to Frontiers, it is not mandatory to use Frontiers .cls files nor frontiers.tex  %
% This will only generate the Manuscript, the final article will be typeset by Frontiers after acceptance.
%                                              %
%                                                                                                                                                         %
% When submitting your files, remember to upload this *tex file, the pdf generated with it, the *bib file (if bibliography is not within the *tex) and all the figures.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%% Version 3.4 Generated 2018/06/15 %%%
%%% You will need to have the following packages installed: datetime, fmtcount, etoolbox, fcprefix, which are normally inlcuded in WinEdt. %%%
%%% In http://www.ctan.org/ you can find the packages and how to install them, if necessary. %%%

\documentclass[utf8]{frontiersSCNS}

%\setcitestyle{square} % for Physics and Applied Mathematics and Statistics articles
\usepackage{url,hyperref,lineno,microtype,subcaption}
\usepackage[onehalfspacing]{setspace}

\linenumbers

% BELOW TAKEN FROM rticles plos template
%
% amsmath package, useful for mathematical formulas
\usepackage{amsmath}
% amssymb package, useful for mathematical symbols
\usepackage{amssymb}

% hyperref package, useful for hyperlinks
\usepackage{hyperref}

% graphicx package, useful for including eps and pdf graphics
% include graphics with the command \includegraphics
\usepackage{graphicx}

% Sweave(-like)
\usepackage{fancyvrb}
\DefineVerbatimEnvironment{Sinput}{Verbatim}{fontshape=sl}
\DefineVerbatimEnvironment{Soutput}{Verbatim}{}
\DefineVerbatimEnvironment{Scode}{Verbatim}{fontshape=sl}
\newenvironment{Schunk}{}{}
\DefineVerbatimEnvironment{Code}{Verbatim}{}
\DefineVerbatimEnvironment{CodeInput}{Verbatim}{fontshape=sl}
\DefineVerbatimEnvironment{CodeOutput}{Verbatim}{}
\newenvironment{CodeChunk}{}{}

% cite package, to clean up citations in the main text. Do not remove.
\usepackage{cite}

\usepackage{color}

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

% Below is from frontiers
%
\bibliographystyle{frontiersinSCNS}
% Use doublespacing - comment out for single spacing
%\usepackage{setspace}
%\doublespacing

% Leave a blank line between paragraphs instead of using \\

\def\keyFont{\fontsize{8}{11}\helveticabold }

%% ** EDIT HERE **
%% PLEASE INCLUDE ALL MACROS BELOW

%% END MACROS SECTION

%\usepackage[table]{xcolor}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}

\def\Authors{
  First Author\,\textsuperscript{1},
  Co-Author\,\textsuperscript{2},
  Co-Author\,\textsuperscript{1,3*}}

\def\Address{

  \textsuperscript{1} Department X, Institution X,  City X,  State XX,  Country X

  \textsuperscript{2} Department X, Institution X,  City X,  State XX,  Country X

  \textsuperscript{3} Department X, Institution X,  City X,  State XX,  Country X
  }

  \def\firstAuthorLast{LASTNAME {et~al.}}

  \def\corrAuthor{Co-Author}\def\corrAddress{Laboratory X, Institute X, Department X, Organization X\\Street X\\City X, State XX, Zip Code X Country X}\def\corrEmail{\href{mailto:email@uni.edu}{\nolinkurl{email@uni.edu}}}

\begin{document}
\onecolumn
\firstpage{1}

\title[Short Title]{Article Title}
\author[\firstAuthorLast]{\Authors}
\address{} %This field will be automatically populated
\correspondance{} %This field will be automatically populated

\extraAuth{}% If there are more than 1 corresponding author, comment this line and uncomment the next one.
%\extraAuth{corresponding Author2 \\ Laboratory X2, Institute X2, Department X2, Organization X2, Street X2, City X2 , State XX2 (only USA, Canada and Australia), Zip Code2, X2 Country X2, email2@uni2.edu}

\maketitle

\begin{abstract}

Abstract length and content varies depending on article type. Refer to 
\url{http://www.frontiersin.org/about/AuthorGuidelines} for abstract requirement
and length according to article type.

%All article types: you may provide up to 8 keywords; at least 5 are mandatory.
\tiny
 \keyFont{ \section{Keywords:} Text Text Text Text Text Text Text Text }

\end{abstract}

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

Hello, how are we doing?

@@

\caption{\label{tab:cleanup-table}Number of removed annotations during cleanup.}
\centering
\begin{tabular}{llrr}
\toprule
Genome & Dataset & Obsolete Annotations & Duplicates\\
\midrule
\rowcolor{gray!6}  Triticum\_aestivum & GOMAP & 285 & 0\\
\cmidrule{1-4}
Hordeum\_vulgarum & GOMAP & 101 & 0\\
\cmidrule{1-4}
\rowcolor{gray!6}  Glycine\_max & GOMAP & 203 & 0\\
\cmidrule{1-4}
Arachis\_hypogaea & GOMAP & 0 & 0\\
\cmidrule{1-4}
\rowcolor{gray!6}  Zea\_mays.PH207 & GOMAP & 798 & 76\\
\cmidrule{1-4}
Zea\_mays.Mo17 & GOMAP & 726 & 77\\
\cmidrule{1-4}
\rowcolor{gray!6}  Phaseolus\_vulgaris & GOMAP & 0 & 0\\
\cmidrule{1-4}
Vigna\_unguiculata & GOMAP & 0 & 0\\
\cmidrule{1-4}
\rowcolor{gray!6}  Medicago\_truncatula.R108 & GOMAP & 0 & 0\\
\cmidrule{1-4}
Zea\_mays.B73.v3 & GOMAP & 1107 & 70\\
\cmidrule{1-4}
\rowcolor{gray!6}  Zea\_mays.W22 & GOMAP & 754 & 82\\
\cmidrule{1-4}
Medicago\_truncatula.A17 & GOMAP & 0 & 0\\
\cmidrule{1-4}
\rowcolor{gray!6}  Zea\_mays.B73.v4 & GOMAP & 752 & 83\\
\cmidrule{1-4}
 & GoldStandard & 38 & 556\\

\rowcolor{gray!6}  \multirow{-2}{*}{\raggedright\arraybackslash Oryza\_sativa} & GOMAP & 111 & 2\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:annotation-quantities}Quantitative metrics of the cleaned functional annotation sets. C, F, P, and A refer to the aspects of the GO: Cellular Component, Biological Function, Molecular Process, and Any/All.}
\centering
\resizebox{\linewidth}{!}{
\begin{threeparttable}
\begin{tabular}{lrlrrr>{\bfseries}r|rrr>{\bfseries}r|rrr>{\bfseries}r}
\toprule
\multicolumn{3}{c}{ } & \multicolumn{4}{c}{Annotations\textsuperscript{a}} & \multicolumn{4}{c}{Annotated Genes [\%]\textsuperscript{b}} & \multicolumn{4}{c}{Median Ann. per G.\textsuperscript{c}} \\
\cmidrule(l{3pt}r{3pt}){4-7} \cmidrule(l{3pt}r{3pt}){8-11} \cmidrule(l{3pt}r{3pt}){12-15}
Genome & Genes & Dataset & C & F & P & A & C & F & P & A & C & F & P & A\\
\midrule
\rowcolor{gray!6}  Arachis\_hypogaea &  & GOMAP & 153433 & 132944 & 493799 & 780176 & 576.67 & 568.55 & 671.23 & 671.24 & 2 & 2 & 6 & 10\\

Glycine\_max &  & GOMAP & 129215 & 113827 & 417555 & 660597 & 460.20 & 470.34 & 528.71 & 528.72 & 2 & 2 & 6 & 11\\

\rowcolor{gray!6}  Hordeum\_vulgarum &  & GOMAP & 88130 & 80282 & 272823 & 441235 & 352.37 & 364.70 & 397.33 & 397.34 & 2 & 2 & 5 & 10\\

Medicago\_truncatula.A17 &  & GOMAP & 107362 & 99719 & 364065 & 571146 & 423.25 & 437.36 & 504.43 & 504.44 & 2 & 2 & 6 & 10\\

\rowcolor{gray!6}  Medicago\_truncatula.R108 &  & GOMAP & 112343 & 108031 & 382322 & 602696 & 403.32 & 502.20 & 557.06 & 557.06 & 1 & 2 & 5 & 9\\

 &  & GOMAP & 72780 & 64685 & 248700 & 386165 & 286.19 & 298.53 & 358.24 & 358.25 & 2 & 2 & 6 & 9\\

\rowcolor{gray!6}  \multirow{-2}{*}{\raggedright\arraybackslash Oryza\_sativa} &  & GoldStandard & 7730 & 11060 & 19378 & 38176 & 57.25 & 73.83 & 90.31 & 113.87 & 1 & 1 & 1 & 3\\

Phaseolus\_vulgaris &  & GOMAP & 72005 & 64583 & 229630 & 366218 & 259.34 & 255.39 & 274.32 & 274.33 & 2 & 2 & 6 & 11\\

\rowcolor{gray!6}  Triticum\_aestivum &  & GOMAP & 267741 & 218623 & 785960 & 1272324 & 956.04 & 981.87 & 1078.90 & 1078.91 & 2 & 2 & 6 & 10\\

Vigna\_unguiculata &  & GOMAP & 75867 & 68313 & 243278 & 387458 & 271.73 & 271.24 & 297.72 & 297.73 & 2 & 2 & 6 & 11\\

\rowcolor{gray!6}  Zea\_mays.B73.v3 &  & GOMAP & 135211 & 87420 & 291251 & 513882 & 348.66 & 380.73 & 394.68 & 394.69 & 3 & 2 & 6 & 11\\

Zea\_mays.B73.v4 &  & GOMAP & 88827 & 82251 & 278719 & 449797 & 367.17 & 373.37 & 393.23 & 393.24 & 2 & 2 & 6 & 10\\

\rowcolor{gray!6}  Zea\_mays.Mo17 &  & GOMAP & 87567 & 79214 & 277787 & 444568 & 336.18 & 351.05 & 386.19 & 386.20 & 2 & 2 & 6 & 10\\

Zea\_mays.PH207 &  & GOMAP & 90617 & 85500 & 288677 & 464794 & 351.70 & 367.62 & 405.56 & 405.57 & 2 & 2 & 6 & 10\\

\rowcolor{gray!6}  Zea\_mays.W22 & \multirow{-15}{*}{\raggedleft\arraybackslash 100} & GOMAP & 95390 & 85039 & 289780 & 470209 & 369.87 & 376.85 & 406.89 & 406.90 & 2 & 2 & 6 & 10\\
\bottomrule
\end{tabular}
\begin{tablenotes}
\item[a] How many annotations in the C, F, and P aspect does this dataset contain? A = How many in total? $A = C + F + P$
\item[b] How many genes in the genome have at least one GO term from the C, F, P aspect annotated to them? A = How many at least one from any aspect? ($A = C \cup F \cup P$)
\item[c] Take a typical gene that is present in the annotation set. How many annotations does it have in each aspect? A = How many in total? Ask your favorite statistician why $A \neq C + F +P$
\end{tablenotes}
\end{threeparttable}}
\end{table}

### 2019-08-18 text/index.Rmd
Use Frontiers template

---
title: "This is the title"
author: "The Pickles"
date: "Febcember 32nd 3023"
language: en-US
site: "bookdown::bookdown_site"
output:
  bookdown::pdf_book:
    keep_tex: true
    keep_md: true
    includes:
      in_header:
        preamble.tex
documentclass: book
---

@@

>>>>

---
title: "Article Title"
runtitle: "Short Title"
documentclass: frontiersSCNS  # or frontiersHLTH, or frontiersFPHY
author:
  - name: First Author
    affiliation: '1'
    etal: LASTNAME # First author's last name. 
  - name: Co-Author
    affiliation: '2'
  - name: Co-Author
    affiliation: '1,3'
    email: email@uni.edu # Indicates corresponding Author
    institution: Laboratory X, Institute X, Department X, Organization X
    street: Street X
    city: City X
    state: State XX # only USA, Australia, Canada
    zip: Zip Code X
    country: Country X
affiliation:
  - id: '1'
    department: Department X
    institution: Institution X
    city: City X
    state: State XX # only USA, Australia, Canada
    country: Country X
  - id: '2' 
    department: Department X
    institution: Institution X
    city: City X
    state: State XX # only USA, Australia, Canada
    country: Country X
  - id: '3' 
    department: Department X
    institution: Institution X
    city: City X
    state: State XX # only USA, Australia, Canada
    country: Country X
date: "Febcember 32nd 3023"
language: en-US
site: "bookdown::bookdown_site"
csl: frontiers.csl
bibliography: test.bib
output:
  bookdown::pdf_book:
    keep_tex: true
    keep_md: true
    base_format: rticles::frontiers_article
    includes:
      in_header:
        preamble.tex
---

@@

\begin{abstract}

Abstract length and content varies depending on article type. Refer to 
\url{http://www.frontiersin.org/about/AuthorGuidelines} for abstract requirement
and length according to article type.

%All article types: you may provide up to 8 keywords; at least 5 are mandatory.
\tiny
 \keyFont{ \section{Keywords:} Text Text Text Text Text Text Text Text }

\end{abstract}
